---
title: "README"
author: "Hari Narayan Sanadhya"
date: "February 14, 2017"
output: 
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Rolling Data Sales - examine housing sales data set of Brooklyn 

## Project Purpose
Using the Rolling Data Sales website, download and examine housing sales data set of Brooklyn. This include cleansing of the data and then analyse it.

## Project Folder and File structure
* Folders:- 

  1. Source Directory:- This folder contains the R source code used to analyze the Rolling Sales Data.

  2. Data:- This folder contains the original data downloaded from the Rolling Data Sales website.

  3. Paper:- This folder contains file that explains the result of the analysis and information regarding any meaningful pattern observed during analysis.

* Files:-

  1. source/R_rollingsales_brooklyn.R:- R code that reads the dataset present in the data folder and perfrom analysis on it.

  2. data/rollingsales_brooklyn.xls:- The original data file downloaded from the Rolling Data Sales website.
  
  3. data/rollingsales_brooklyn.csv:- The csv data file generated from the original downloaded file from the Rolling Data Sales website. ONly the type of the file changed, no other changes made.

  4. paper/patterns.md:- This file contains the result of the analysis and information regarding meaningful patterns observed during analysis.

  5. README.md:- This file includes an explanation of the purpose of the project and the other files.



# Session Information
```{r echo=FALSE}
sessionInfo()
```

